Detecting threats of violence in YouTube comments

### 2016-02-10 submission.tex
More previous work

\newcite{dinakar2011} proposes a method for the detection of
cyberbullying by targeting combinations of profane or negative words,
and words related to several predetermined sensitive topics. Their
data set consists of over 50,000 YouTube comments taken from videos
about controversial topics. The topics included sexuality, race,
culture and intelligence. The comments were grouped by topic, and then
12~\% of these were manually annotated to check that they were placed
in the right category.

The first stage of the detection was the same across all
categories. It consisted of using a lexicon of negative words and a
list of profane words, as well as part-of-speech tags from the
training data that were correlated with bullying. The second stage was
category-specific, and used commonly observed uni- and bigrams from
each category as features. The experiments reported accuracies from
63~\% to 80~\%, but did not report precision or recall.

@@

\begin{figure}[h]
\begin{verbatim}
timpa666
1    and i will kill every fucking muslim and arab!

@@

\end{verbatim}
\caption{Examples of comments from the data set.}
\label{fig:comments}
\end{figure}

>>>>

\newcite{dinakar2011} proposes a method for the detection of
cyberbullying by targeting combinations of profane or negative words,
and words related to several predetermined sensitive topics. Their
data set consists of over 50,000 YouTube comments taken from videos
about controversial topics. The topics included sexuality, race,
culture and intelligence. The comments were grouped by topic, and then
12~\% of these were manually annotated to check that they were placed
in the right category.
The first stage of the detection was the same across all
categories. It consisted of using a lexicon of negative words and a
list of profane words, as well as part-of-speech tags from the
training data that were correlated with bullying. The second stage was
category-specific, and used commonly observed uni- and bigrams from
each category as features. The experiments reported accuracies from
63~\% to 80~\%, but did not report precision or recall.

There has been quite a bit of work focused on the detection of threats
in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}.
The data set used for these experiments consisted a collection of 5000
threatening tweets collected by a website over a period of about two
years. In addition, a large number of random tweets were collected for
development and testing. A set of 2.3 million random tweets was used
for development, and a set of 1 million was used for testing. This set
was not annotated in any way prior to being used in the experiments.
The system relies on manually constructed recognition patterns, in the
form of n-grams (uni-, bi- and trigrams, as well as skip bi- and
trigrams), but do not go into detail about the methods used to
construct these patterns, stating that the researchers relied on their
(linguistic) intuition as speakers of Dutch \cite{nellngram2013}. In
\newcite{nellshallow2013}, a manually crafted shallow parser is added
to the system. This improves results to a precision of 39\% and a
recall of 59\%.

\newcite{warner2012} present a method for detecting unwanted or
illegal comments in user-generated web text from the internet, which
relies on machine learning in combination with template-based
features. The data set used in the research came from two sources. The
first consists of posts from Yahoo news groups, the second were
webpages collected by the American Jewish Congress that had been
identified as offensive. The data set was manually annotated, and then
the hate speech was assigned to a category, such as antisemitic,
anti-woman, anti-asian, etc. The research then focused on the
antisemitic category.  The research approaches the problem as a
word-sense disambiguation task, since the same words can be used in
both hateful and non-hateful contexts. The features used in the
classification were combinations of uni-, bi- and trigrams,
part-of-speech-tags and Brown clusters.  The best results of the
classifications were obtained using only unigrams as features, with a
precision of 67~\% and a recall of 60~\%. The other feature sets
garnered much lower results, and the authors suggest that deeper
parsing could reveal significant phrase patterns.

@@

\begin{figure*}[h]
\begin{verbatim}
timpa666
1    and i will kill every fucking muslim and arab!

@@

\end{verbatim}
\caption{Examples of comments from the data set.}
\label{fig:comments}
\end{figure*}
